Enter our title here

### 2017-09-11 manuscript.tex
edited intro

The purpose of this paper is to introduce a relatively new interactive teaching tool, DataCamp, which incorporates only the best
qualities from the tools mentioned above.

@@

@@

All DataCamp courses will have a course badge and most will use data sets and R packages. Information on how to add data sets and images
can be found in DataCamps 'Teach' documentation \url{https://www.datacamp.com/teach/documentation} under the 'Upload Assets' tab. However,
there is currently no information on DataCamp about integrating R packages. To use R packages in a course, you will need to create a new file
in the GitHub course repository named 'requirements.r'. The file should contain: $devtools::install_version$, package name and version for every
package you use in the DataCamp course. For example, following code will add the 'ggplot2' and 'mosaic' packages to the repository.

$$devtools::install_version("ggplot2", "2.2.0")$$
$$devtools::install_version("mosaic", "0.14.4")$$

In order for DataCamp to recognize this new file, you will need to add $$from: r-base-prod:27$$ to the course.yml file.

>>>>

The purpose of this article is to introduce a relatively new technology, DataCamp, which incorporates the best
qualities from the teaching tools mentioned above.

@@

\begin{verbatim}
--- type:PlainMultipleChoiceExercise lang:r xp:50 skills:1 key:9707072219
## Quick check 2

What can R be used for?

*** =instructions
- Graphing data
- Analyzing data
- Calculations
- All of the above

*** =hint
R software can be used for all of these things.

*** =pre_exercise_code
```{r}

```

*** =sct
```{r}

msg_bad <- "That is not correct"
msg_success <- "Exactly! R can do all of these things."
test_mc(correct = 4, feedback_msgs = c(msg_bad, msg_bad, msg_bad, msg_success))
```

\end{verbatim}

@@

All DataCamp courses will have a course badge and most will use data sets and R packages. Information on how to add data sets and images
can be found in DataCamps 'Teach' documentation \url{https://www.datacamp.com/teach/documentation} under the 'Upload Assets' tab. However,
there is currently no information on DataCamp about integrating R packages. To use R packages in a course, you will need to create a new file
in the GitHub course repository named \texttt{requirements.r}. The file should contain: \texttt{devtools::install\_version}, package name and version for every
package you use in the DataCamp course. For example, following code will add the \texttt{ggplot2} and \texttt{mosaic} packages to the repository.

\begin{verbatim}
devtools::install_version("ggplot2", "2.2.0")
devtools::install_version("mosaic", "0.14.4")
\end{verbatim}
In order for `DataCamp' to recognize this new file, you will need to add $$from: r-base-prod:27$$ to the course.yml file.
